### 2013-06-24 trunk/network-science/paper.tex

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploited the basic form of
quantification to concentrate on specific features of the whole graph, or an
individual vertex. Our work is to promote this methodology to the dynamic
graphs. We basically design new dynamic metrics according to existing
successful static ones, but we will point out a important metric that can be
only observed in time evolving networks, the activity. Intuitively speaking,
a vertex with high activity indicates more frequent recent social actions, and
the vertex is more willing to make new change by the structural sense of graph.
The accuracy of activity will be quite vital to recommendation algorithms of
advertisement, new friends, or search results. Activity can be also used by
other metrics, so that the computation of other metrics will no longer need the
time information directly, but referring to the activity instead.

@@

\begin{observation} $K=O(1)$.
\end{observation}
So if we only use the reduced edge list in our framework as additional memory
requirements, or similarly speaking, consider the adjacency matrix to be a
sparse matrix and only store the non-zero entries, the space expense would then
be just $O(n)$, which is highly available. However this does not means we can
handle neighbor updating operations in $O(1)$ time, because
\begin{equation}\max k^\bullet\geq
\left<k^\bullet\right>=K \end{equation} and the former one may be very large.
We cannot trivially assert the amortized time complexity to be $O(1)$ neither,
because the nodes with high degrees may requires more operations over time,
just like the famous friendship paradox\cite{feld1991your}.

@@

\begin{center} \begin{tikzpicture}[y=.3cm, x=.3cm, font=\sffamily]
  \begin{axis}[ 
    xlabel={$z$},
    ylabel={$a$}
  ] 
    \addplot[domain=-10:-0.001] {exp(ln(10)*(1/x))}; 
  \end{axis}
\end{tikzpicture} \end{center}

@@

\subsection{Program}
We have implemented the algorithms using C++ language without compiler
optimization, and all execution is done under a typical PC with Intel Core i3.

>>>>

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploited the basic form of
quantification to concentrate on specific features of the whole graph, or an
individual vertex. Our work is to promote this method to the dynamic graphs. We
basically design new dynamic metrics according to existing successful static
ones, but we will point out a important metric that can be only observed in
time evolving networks, the activity. Intuitively speaking, a vertex with high
activity indicates more frequent recent social actions, and the vertex is more
willing to make new change by the structural sense of graph.  The accuracy of
activity will be quite vital to recommendation algorithms of advertisement, new
friends, or search results. Activity can be also used by other metrics, so that
the computation of other metrics will no longer need the time information
directly, but referring to the activity instead.

@@

\begin{observation} $K=O(1)$.
\end{observation}
So if we only use the reduced edge list in our framework as additional memory
requirements, namely considering the adjacency matrix to be a sparse matrix and
only store the non-zero entries, the space expense would then be just $O(n)$,
which is highly available. However this does not means we can handle neighbor
updating operations in $O(1)$ time, because
\begin{equation}
\max k^\bullet\geq \left<k^\bullet\right>=K
\end{equation}
and the former one may be very large.  We cannot trivially assert the amortized
time complexity to be $O(1)$ neither, because the nodes with high degrees may
requires more operations over time, just like the famous friendship
paradox\cite{feld1991your}.

@@

\begin{center} \begin{tikzpicture}
  \begin{axis}[ 
    xlabel={$z$},
    ylabel={evolving activity}
  ] 
  \addplot[color=blue!50!black,samples=300,domain=-20:-0.001] {exp(ln(10)*(1/x))}; 
  \addplot[color=green!50!black,samples=300,domain=-20:-0.001] {exp(ln(100)*(1/x))}; 
  \addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
  \end{axis}
\end{tikzpicture}

\begin{color}{blue!50!black}blue
\end{color}: $\mu=10$,
\begin{color}{green!50!black}green
\end{color}: $\mu=100$,
\begin{color}{red!50!black}red
\end{color}: $\mu=1000$\end{center}

@@

\subsection{Program}
We have implemented the algorithms using C++ language without compiler
optimization, and all execution is done under a typical PC with Intel Core i3
M380.
